\sysfull

### 2018-04-17 paper/coalescing.tex
Final pass on coalescing

A key limitation of this algorithm lies in the equality of the target decrease
in $f_\text{reboot}(B)$ and the increase in $f_\text{reboot}(B)$.  If, after
some number $k$ successful commits the target must decrease back to its
original value before the $k$ commits, the algorithm must then decrease $B$ by
$k \times x$.  To accumulate this decrease, this strategy requires $k$ power
failures, after each of which the strategy decreases $B$ by $x$, eventually
decreasing by $k \times x$, but only after a long time.

@@

The History-Guided (HG) coalescing strategy adapts the coalescing target more
quickly, addressing a key limitation of the EO coalescing strategy.  
%
EA gives each task unity weight, as with EO.  
%
HG differs from EO in how it updates $B$ on commit, and after a power failure.
%
HG assumes that as the duration of execution since a power failure increases,
the amount of energy remaining decreases, and the risk of failing during a long
sequence of coalesced tasks increases.  
%
Consequently, HG decreases the coalescing target by half with each successful commit.
%
HG is {\em history-guided} because it initializes the coalescing target to be
equal to $H$, the total number of tasks executed between the most recent pair
of power failures.
%
While a history of $H$ suggests that there is sufficient energy to coalesce and
successfully commit $H$ tasks (i.e., to set $B = H$), HG conservatively sets $B$ equal to half
of $H$ moderating the risk of a very long coalesced task. 
%
The fraction of the history by which HG adjusts $B$ is arbitrary.
We experimented with a range of fraction values, settling on one half as the
default for HG, because one half had the highest performance.

@@

The EA algorithm is characterized by the following functions:

>>>>

A key limitation of this algorithm lies in the equality of the target decrease
in $f_\text{reboot}(B)$ and the increase in $f_\text{commit}(B)$.  If, after
some number $k$ successful commits the target must decrease back to its
original value before the $k$ commits, the algorithm must then decrease $B$ by
$k \times x$.  To accumulate this decrease, this strategy requires $k$ power
failures, after each of which the strategy decreases $B$ by $x$, eventually
decreasing by $k \times x$, but only after a long time.

@@

The History-Guided (HG) coalescing strategy adapts the coalescing target more
quickly, addressing a key limitation of the EO coalescing strategy.  
%
HG gives each task unity weight, as with EO.  
%
HG differs from EO in how it updates $B$ on commit, and after a power failure.
%
HG assumes that as the duration of execution since a power failure increases,
the amount of energy remaining decreases, and the risk of failing during a long
sequence of coalesced tasks increases.  
%
Consequently, HG decreases the coalescing target by half with each successful commit.
%
HG is {\em history-guided} because it initializes the coalescing target to be
equal to $H$, the total number of tasks executed between the most recent pair
of power failures.
%
While a history of $H$ suggests that there is sufficient energy to coalesce and
successfully commit $H$ tasks (i.e., to set $B = H$), HG conservatively sets $B$ equal to half
of $H$ moderating the risk of a very long coalesced task. 
%
The fraction of the history by which HG adjusts $B$ is arbitrary.
We experimented with a range of fraction values, settling on one half as the
default for HG, because one half had the highest performance.

@@

The HG algorithm is characterized by the following functions:
